Estimating Output Loss due to being Unrecognized as States

### 2019-03-07 paper/paper.tex
Describe the economic situations of Karabakh #51

One consequence of the War of Secession is ethnic homogenization on both sides of the border. It is estimated that approximately 500,000 Azerbaijanis were displaced from the occupied part of Azerbaijan while 353,000 Armenians were displaced from the rest of Azerbaijan.%
\footnote{
	These numbers are based on Arif Yunusov's calculations, cited by de Waal (2013: 327).
}
\section{Data}
\subsection{Real GDP}
We use the Penn World Table 9.0 (Freenstra et al.\ 2015), as the data source for real GDP. 
Expenditure-side real GDP at chained PPPs in 2011 US dollars (the variable \textit{rgdpe}) is used because the variable is meant for comparing ``living standards across countries and across years'' (Freenstra et al.\ 2015, Table 1).

@@

\begin{thebibliography}{99}                                                                                                %
\bibitem{} Alesina, Alberto, Stelios Michalopoulos, and Elias Papaioannou. 2016. ``Ethnic Inequality.'' \textit{Journal of Political Economy}, 124(2): 428-488.
\bibitem{} Bickenbach, Frank, Eckhardt Bode, Peter Nunnenkamp, and Mareike Soder. 2016. ``Night lights and regional GDP.'' \textit{Review of World Economics}, 152 (2), 425-447.                                                                                         
\bibitem{} Cameron, A. Colin, Jonah B. Gelbach, and Douglas L. Miller. 2011. ``Robust Inference With Multiway Clustering.'' \textit{Journal of Business \& Economic Statistics}, 29(2): 238-249.
\bibitem{} de Waal, Thomas. 2013. \textit{Black Garden: Armenia and Azerbaijan through Peace and War} (Revised Edition). New York: New York University Press.
\bibitem{} Dreher, Axel, Andreas Fuchs, Roland Hodler, Bradley C. Parks, Paul A. Raschky, and Michael J. Tierney. 2015. ``Aid on Demand: African Leaders and the Geography of China?s Foreign Assistance.'' CEPR Discussion Paper, 10170.
\bibitem{} Feenstra, Robert C., Robert Inklaar, and Marcel P. Timmer. 2015. ``The Next Generation of the Penn World Table.'' \textit{American Economic Review}, 105(10): 3150-3182.
\bibitem{} GADM. 2018. ``GADM Maps and Data (version 3.6).'' https://gadm.org (accessed February 7, 2019).
\bibitem{} Goldblatt, Ran, Kilian Heilmann, and Yonatan Vaizman. 2018. ``Can Medium-Resolution Satellite Imagery Measure Economic Activity at Small Geographies? Evidence from Landsat in Vietnam.'' \textit{World Bank Economic Review}, forthcoming.
\bibitem{} Henderson, J. Vernon, Adam Storeygard, and David N. Weil. 2012. ``Measuring Economic Growth from Outer Space.'' \textit{American Economic Review}, 102(2): 994-1028.
\bibitem{} Hodler, Roland, and Paul A. Raschky. 2014. ``Regional Favoritism.'' \textit{Quarterly Journal of Economics}, 129(2): 995-1033.
\bibitem{} Mellander, Charlotta, Jose Lobo, Kevin Stolarick, and Zara Matheson. 2015. ``Night-Time Light Data: A Good Proxy Measure for Economic Activity?'' \textit{PloS one}, 10(10), e0139779.
\bibitem{} National Geophysical Data Center. 2015. ``Version 4 DMSP-OLS Nighttime Lights Time Series.'' National Oceanic and Atmospheric Administration. https://ngdc.noaa.gov/eog/dmsp/downloadV4composites.html (accessed February 6, 2019).
\bibitem{} Pinkovskiy, Maxim, and Xavier Sala-i-Martin. 2016. ``Newer Need Not be Better: Evaluating the Penn World Tables and the World Development Indicators Using Nighttime Lights.''. NBER Working Paper, 22216.
\bibitem{} Storeygard, Adam. 2016. ``Farther on down the Road: Transport Costs, Trade and Urban Growth in Sub-Saharan Africa.'' \textit{The Review of Economic Studies}, 83(3): 1263-1295.
\bibitem{} Witmer, Frank D.W., and John O?Loughlin. 2011. ``Detecting the Effects of Wars in the Caucasus Regions of Russia and Georgia Using Radiometrically Normalized DMSP-OLS Nighttime Lights Imagery.'' \textit{GIScience \& Remote Sensing}, 48(4): 478-500.
\bibitem{} World Bank. 2018. \textit{World Development Indicators}. http://wdi.worldbank.org (accessed February 27, 2019).
\end{thebibliography}

>>>>

One consequence of the War of Secession is ethnic homogenization on both sides of the border. It is estimated that approximately 500,000 Azerbaijanis were displaced from the occupied part of Azerbaijan while 353,000 Armenians were displaced from the rest of Azerbaijan.%
\footnote{
	These numbers are based on Arif Yunusov's calculations, cited by de Waal (2013: 327).
}

Information is scant on economic conditions in Nagorno-Karabakh since the 1994 ceasefire. 
International Crisis Group (2005: 14-15) provides a rare account of Karabakh's economy as follows. 
\begin{itemize}
\item Entrepreneurs have been engaged in profitable scrap metal businesses by dismantling infrastructure, housing and other pre-war structures for the resale of metal, bricks and building materials in the occupied territory of Azerbaijan.
\item Privatization of land and state enterprises has largely been completed. All residents outside the capital city of Stepanakert received 0.6 hectares of arable land. Private companies account for 80\% of the output. 
\item Under-employment is widespread among rural residents although officials claim that the unemployment rate was 5.6\% in 2003. In 2005, the government started providing the unemployed with 60\% of the minimum wage.
\item The government encourages child birth through various benefits for children: large families receive free electricity and books; couples with three children or more receive cash grants; and those with six children or more are given new homes.
\item Income inequality is growing. In a survey of 1,000 by Stepanakert Press Club in October 2003, 40.5\% of the respondents answered that they lived better than five years ago while 57.6\% said their life got worse or didn't change.
\end{itemize}

\section{Data}
\subsection{Real GDP}
We use the Penn World Table 9.0 (Freenstra et al.\ 2015), as the data source for real GDP. 
Expenditure-side real GDP at chained PPPs in 2011 US dollars (the variable \textit{rgdpe}) is used because the variable is meant for comparing ``living standards across countries and across years'' (Freenstra et al.\ 2015, Table 1).

@@

\begin{thebibliography}{99}                                                                                                %
\bibitem{} Alesina, Alberto, Stelios Michalopoulos, and Elias Papaioannou. 2016. ``Ethnic Inequality.'' \textit{Journal of Political Economy}, 124(2): 428-488.
\bibitem{} Bickenbach, Frank, Eckhardt Bode, Peter Nunnenkamp, and Mareike Soder. 2016. ``Night lights and regional GDP.'' \textit{Review of World Economics}, 152 (2), 425-447.                                                                                         
\bibitem{} Cameron, A. Colin, Jonah B. Gelbach, and Douglas L. Miller. 2011. ``Robust Inference With Multiway Clustering.'' \textit{Journal of Business \& Economic Statistics}, 29(2): 238-249.
\bibitem{} de Waal, Thomas. 2013. \textit{Black Garden: Armenia and Azerbaijan through Peace and War} (Revised Edition). New York: New York University Press.
\bibitem{} Dreher, Axel, Andreas Fuchs, Roland Hodler, Bradley C. Parks, Paul A. Raschky, and Michael J. Tierney. 2015. ``Aid on Demand: African Leaders and the Geography of China?s Foreign Assistance.'' CEPR Discussion Paper, 10170.
\bibitem{} Feenstra, Robert C., Robert Inklaar, and Marcel P. Timmer. 2015. ``The Next Generation of the Penn World Table.'' \textit{American Economic Review}, 105(10): 3150-3182.
\bibitem{} GADM. 2018. ``GADM Maps and Data (version 3.6).'' https://gadm.org (accessed February 7, 2019).
\bibitem{} Goldblatt, Ran, Kilian Heilmann, and Yonatan Vaizman. 2018. ``Can Medium-Resolution Satellite Imagery Measure Economic Activity at Small Geographies? Evidence from Landsat in Vietnam.'' \textit{World Bank Economic Review}, forthcoming.
\bibitem{} Henderson, J. Vernon, Adam Storeygard, and David N. Weil. 2012. ``Measuring Economic Growth from Outer Space.'' \textit{American Economic Review}, 102(2): 994-1028.
\bibitem{} Hodler, Roland, and Paul A. Raschky. 2014. ``Regional Favoritism.'' \textit{Quarterly Journal of Economics}, 129(2): 995-1033.
\bibitem{} International Crisis Group. 2005. ``Nagorno-Karabakh: Viewing the Conflict from the Ground.'' Crisis Group Europe Report, no.\ 166.
\bibitem{} Mellander, Charlotta, Jose Lobo, Kevin Stolarick, and Zara Matheson. 2015. ``Night-Time Light Data: A Good Proxy Measure for Economic Activity?'' \textit{PloS one}, 10(10), e0139779.
\bibitem{} National Geophysical Data Center. 2015. ``Version 4 DMSP-OLS Nighttime Lights Time Series.'' National Oceanic and Atmospheric Administration. https://ngdc.noaa.gov/eog/dmsp/downloadV4composites.html (accessed February 6, 2019).
\bibitem{} Pinkovskiy, Maxim, and Xavier Sala-i-Martin. 2016. ``Newer Need Not be Better: Evaluating the Penn World Tables and the World Development Indicators Using Nighttime Lights.''. NBER Working Paper, 22216.
\bibitem{} Storeygard, Adam. 2016. ``Farther on down the Road: Transport Costs, Trade and Urban Growth in Sub-Saharan Africa.'' \textit{The Review of Economic Studies}, 83(3): 1263-1295.
\bibitem{} Witmer, Frank D.W., and John O?Loughlin. 2011. ``Detecting the Effects of Wars in the Caucasus Regions of Russia and Georgia Using Radiometrically Normalized DMSP-OLS Nighttime Lights Imagery.'' \textit{GIScience \& Remote Sensing}, 48(4): 478-500.
\bibitem{} World Bank. 2018. \textit{World Development Indicators}. http://wdi.worldbank.org (accessed February 27, 2019).
\end{thebibliography}
